Top Text

### 2022-12-12 Paper.tex
Wrote abstract

	\begin{abstract}
		This is the abstract.

>>>>

	\begin{abstract}
		Following the explosion of artificial intelligence during the year of 2022, there now are many text-to-image generation applications out there. This is great for the field of artificial intelligence as a whole, however it has made knowing which application is best quite hard for artists who are new to text-to-image generation. This paper looks at four of the most popular generators, with the aim to find out which one is the best for an inexperienced artist.
